\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-24 Proposal.tex
updated work packages and evalutation criteria

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase} That said, it is imperative to facilitate knowledge transfer.  Thus, we will examine how visually representing information and its context can make knowledge transfer easier. For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information. We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.

@@

\subsection{WP2: Combining OMDoc and Spatial Narration}

What is the idea?
(half a page)
\newpage

\subsection{WP3: Implement OMDoc examples in Impress.js}
\newpage

\subsection{WP4: Evaluation}

Perform qualitative analysis of the visualization produced by the implementet \sys. Determine whether the implemented \sys meats the goals that were outlined in the Evaluation Criteria. Measure the speed of the system.
\ednote{SMART goals?}
\newpage

>>>>

"Knowledge is the information necessary to support intelligent reasoning." \cite{Kohlhase} That said, it is imperative to facilitate knowledge transfer.  Thus, we will examine how visually representing information and its context can make knowledge transfer easier. For this we will be examining the OMDoc (Open Mathematical Documents) format as the example that will provide us with an annotated set of documents of which we will visualize the dependencies of the contained information. We will however not visualize the dependencies as a simple graph but use an API such as Impress.js to allow for us to show the current piece of information of interest in context with dependent information.\\

@@

\subsection{WP2: Using OMDoc to create ordered information graphs}
The idea is to use the General Computer Science Lecture notes as an experiment. The General Computer Science Lecture notes are an annotated set of documents. Using OMDoc, we will create an information graph out of the annotated set of documents. This information graph should be ordered based on dependencies of knowledge.\\

\subsection{WP3: Combining OMDoc and Spatial Narration}
Once we have an ordered information graph we will visualize the information in different ways and analyze each way. The outcome of the analysis should be a model which we will then use to visualize the information in WP4.\\

\subsection{WP3: Implement OMDoc examples in Impress.js}
After the best model for spatial narration is found, we will implement a system that will take the ordered information graph and transform it into a spatial presentation using Impress.js.

\subsection{WP4: Evaluation}
Once we have results, a qualitative analysis of the visualization produced by the implemented \sys should be perfomed. In addition we will determine whether the implemented \sys meets the goals outlined in the Evaluation Criteria. Lastly we will measure the speed of the system.
